Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-08 Draft/contributions.tex
small typos fixed

At tree--level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha_{ew}^6)$, the QCD background $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ and the interference $\mathcal{O}(\alpha_s\alpha_{ew}^5)$.\\
The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO. EW contribution in red, QCD in green, interference in gray and sum in blue. No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied. Results of full LO matrix element simulation.}
\label{fig:mjjdyjj_1d}
\end{figure*}
Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alpha_s^2\alpha_{ew}^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed. The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions). The LO cross--section for the three perturbative orders are shown in table~\ref{tab:LOscanXsec}.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha_{ew}^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alpha_s^2\alpha_{ew}^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alpha_s\alpha_{ew}^5))$ \\
        \hline
        \hline
        {\sc Phantom}  &  $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
        {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process: these results concern the setup described in section~\ref{subsec:inputpar}, apart from the $M_{jj}$ and $|\Delta y_{jj}|$ cuts which have been dropped.}
\end{table}
The EW, QCD and interference amount respectively to 57\%, 37\% and 6\% of the total inclusive cross section. In the presence of typical VBS cuts, the EW contribution is strongly enhanced, as shown in section~\ref{subsec:LOfiducial}.\\
The EW contribution to the $M_{jj}$ distribution (red curve in Fig.~\ref{fig:mjjdyjj_1d}) shows a huge peak around the $W$ mass: this is due to the possibility for the two jets to be decay products of a $W^-$ boson. Note that this effect doesn't arise in calculations which employ VBS approximation (see VBS approx. description in section [ref.]).
One can also see this in three different plots in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alpha^5\alphas)$ (top right), and $\mathcal{O}(\alpha^4 \alphas^2)$ (bottom).}
\label{fig:mjjdyjj_2d_LO}
\end{figure}

>>>>

At tree level, there are three contributions to the $W^+W^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the QCD background $\mathcal{O}(\alphas^2\alpha^4)$ and the interference $\mathcal{O}(\alphas\alpha^5)$.\\
The three contributions to the the jet--jet invariant mass $M_{jj}$ and positive rapidity difference $|\Delta y_{jj}|$ distributions are shown in Fig.~\ref{fig:mjjdyjj_1d}, together with their sum.
\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/mjj_full.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/dyjj_full.pdf}
\caption{Differential distribution in the jet--jet invariant mass $M_{jj}$ (left) and the positive difference of the jet rapidities $|\Delta y_{jj}|$ (right) at LO. EW contribution in red, QCD in green, interference in gray and sum in blue. No cuts on $M_{jj}$ and $|\Delta y_{jj}|$ are applied. Results of full LO matrix element simulation.}
\label{fig:mjjdyjj_1d}
\end{figure*}
Concerning the QCD contribution, it is worth noticing that for quantum numbers conservation external gluons cannot contribute at LO, thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve $t/u$--channel virtual gluons: this results in a small QCD background, although the VBF topological cuts are not imposed. The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions). The LO cross--section for the three perturbative orders are shown in table~\ref{tab:LOscanXsec}.
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}] (\mathcal{O}(\alpha^6))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas^2\alpha^4))$ & $\sigma[\rm{fb}] (\mathcal{O}(\alphas\alpha^5))$ \\
        \hline
        \hline
        {\sc Phantom}  &  $ 2.292 \pm 0.002 $ & $ 1.477 \pm 0.001 $ & $ 0.223 \pm 0.003 $ \\
        {\sc Xxx}&  $ \pm $ & $ \pm $ & $ \pm $
    \end{tabular}
    \caption{\label{tab:LOscanXsec} Cross sections at LO accuracy for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process: these results concern the setup described in section~\ref{subsec:inputpar}, apart from the $M_{jj}$ and $|\Delta y_{jj}|$ cuts which have been dropped.}
\end{table}
The EW, QCD and interference amount respectively to 57\%, 37\% and 6\% of the total inclusive cross section. In the presence of typical VBS cuts, the EW contribution is strongly enhanced, as shown in section~\ref{subsec:LOfiducial}.\\
The EW contribution to the $M_{jj}$ distribution (red curve in Fig.~\ref{fig:mjjdyjj_1d}) shows a huge peak around the $W$ mass: this is due to the possibility for the two jets to be decay products of a $W^-$ boson. Note that this effect doesn't arise in calculations which employ VBS approximation (see VBS approx. description in section [ref.]).
One can also see this in three different plots in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$.
\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top left), $\mathcal{O}(\alpha^5\alphas)$ (top right), and $\mathcal{O}(\alpha^4 \alphas^2)$ (bottom).}
\label{fig:mjjdyjj_2d_LO}
\end{figure}

### 2018-01-08 Draft/description.tex
typocorr2
small typos fixed

\begin{table*}[ht!]
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
        \hline
        \hline
        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
        {\sc POWHEG}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
\end{table*}

@@

  \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
  and $e^+e^-$ colliders at $\alpha_{ew}^6$ and $\alpha_{ew}^4\alpha_s^2$ including interferences between the two sets of diagrams.
It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity 
formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{BERENDS1985441} and an adaptive
strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}.

@@

% The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alpha_s)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alpha_s)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}
%
%

>>>>

\begin{table*}[ht!]
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Non-res.  & NLO &  NF QCD  &  EW corr. to $\mathcal O(\alphas \alpha^5)$  \\
        \hline
        \hline
        {\sc Bonsay}        &  $t/u$    &  No       &  Yes, virt. No    &  Yes   & No       &  No  \\
        {\sc POWHEG}        &  $t/u$    &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc MG5\_aMC}      &  Yes      &  Yes      &  Yes              &  Yes   & No virt. &  No \\
        {\sc MoCaNLO+Recola}&  Yes      &  Yes      &  Yes              &  Yes   & Yes      &  Yes  \\
        {\sc PHANTOM}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
        {\sc VBFNLO}        &  Yes      &  No       &  Yes              &  Yes   & No       &  No  \\
        {\sc Whizard}       &  Yes      &  Yes      &  Yes              &  No    & -        & - \\  
    \end{tabularx}
    \caption{\label{tab:wg1_codes} Summary of the different properties of the codes employed in the comparison.}
\end{table*}

@@

  \item {{\sc{Phantom}}~\cite{Ballestrero:2007xq} is a dedicated tree--level Monte Carlo for six parton final states at $pp,\, p\bar{p}$
  and $e^+e^-$ colliders at $\alpha_{ew}^6$ and $\alpha_{ew}^4\alphas^2$ including interferences between the two sets of diagrams.
It employs complete tree--level matrix elements in the complex--mass scheme~\cite{Denner:2006ic} computed via the modular helicity 
formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{BERENDS1985441} and an adaptive
strategy~\cite{PETERLEPAGE1978192}. {\sc{Phantom}} generates unweighted events at parton--level for both the SM and a few instances of BSM theories.}

@@

% The complete comparison of the codes will be published in a separate work. Here, we present some preliminary results obtained at LO ($\mathcal O (\alpha^6)$) and including
NLO QCD corrections at fixed-order $\mathcal O (\alpha^6\alphas)$, for the process ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$.
In Tab.~\ref{tab:wg1_codes} the details of the various codes are reported. In particular, it is specified whether
\begin{itemize}
    \item all $s$- and $t/u$-channel diagrams that lead to the considered final state are included;
    \item interferences between diagrams are included at LO;
    \item diagrams which do not feature two resonant vector bosons are included;
    \item the so-called non-factorisable (NF) QCD corrections, that is the corrections where (real or virtual) gluons are exchanged between different quark lines,
        are included;
    \item EW corrections to the $\mathcal O (\alpha^5\alphas)$ interference are included. These corrections are of the same order as the NLO QCD corrections to
        the  $\mathcal O (\alpha^6$) term.
\end{itemize}
%
%

### 2018-01-08 Draft/fiducialregion.tex
small typos fixed

\begin{figure}[hbt]
\centering %jjpeak_diag
\includegraphics[scale=0.19]{figures/scanfigures/jjpeak_diag.png}
\caption{Tree--level $\mathcal{O}(\alpha_{ew}^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha_{ew}^6)$, $\mathcal{O}(\alpha_{ew}^5\alpha_s)$ and $\mathcal{O}(\alpha_{ew}^4 \alpha_s^2)$, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
\end{figure}

\begin{figure}[hbt]
\centering
%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
FIGURE
\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics. Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}
\newpage

@@

The VBS approximation [?] is frequently employed for VBS computations and we aim at the identification of kinematical regions where it provides trustworthy prediction for the $W^+W^+$ scattering.
At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha_{ew}^6)$, the approximations consists in:
\begin{itemize}
\item discarding interferences between $t$ and $u$ channel diagrams, which are expected to be suppressed in the fiducial volume, after VBF cuts;
\item discarding $s$--channel diagrams shown in \autoref{fig:jjpeak_diag}, which contain $q\bar{q}'$ annihilations ($W^-\rightarrow q \bar{q}'$); with a hard cut on the $jj$--pair invariant mass, these contributions are strongly suppressed.
\end{itemize}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{PHANTOM} (full) calculations.}\label{fig:ratio2d_LO}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations. RIGHT SIDE FIG. IN PREPARATION. QUESTION: is RECOLA calc. 'exact' ?}\label{fig:ratio2d_NLO}
\end{figure}

>>>>

\begin{figure}[hbt]
\centering %jjpeak_diag
\includegraphics[scale=0.19]{figures/scanfigures/jjpeak_diag.png}
\caption{Tree--level $\mathcal{O}(\alpha^6)$ diagrams involving a $W^-$ boson decaying into a $q\bar{q}'$ pair.} \label{fig:jjpeak_diag}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at the three leading perturbative orders $\mathcal{O}(\alpha^6)$, $\mathcal{O}(\alpha^5\alphas)$ and $\mathcal{O}(\alpha^4 \alphas^2)$, without any cut on the $jj$ pair kinematics. Results of full matrix element \texttt{RECOLA} calculations.}\label{fig:mjjdyjj_2d_LO}
\end{figure}

\begin{figure}[hbt]
\centering
%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
FIGURE
\caption{Cross section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics. Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}
\newpage

@@

The VBS approximation [?] is frequently employed for VBS computations and we aim at the identification of kinematical regions where it provides trustworthy prediction for the $W^+W^+$ scattering.
At LO, given the full set of diagrams contributing at order $\mathcal{O}(\alpha^6)$, the approximations consists in:
\begin{itemize}
\item discarding interferences between $t$ and $u$ channel diagrams, which are expected to be suppressed in the fiducial volume, after VBF cuts;
\item discarding $s$--channel diagrams shown in \autoref{fig:jjpeak_diag}, which contain $q\bar{q}'$ annihilations ($W^-\rightarrow q \bar{q}'$); with a hard cut on the $jj$--pair invariant mass, these contributions are strongly suppressed.
\end{itemize}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha^6)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{PHANTOM} (full) calculations.}\label{fig:ratio2d_LO}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations. RIGHT SIDE FIG. IN PREPARATION. QUESTION: is RECOLA calc. 'exact' ?}\label{fig:ratio2d_NLO}
\end{figure}

### 2018-01-08 Draft/input.tex
new changes on the draft (very long train ride thanks to DB...)
small typos fixed

We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
density~\cite{Ball:2014uwa}
with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alpha_s\left( \MZ \right) = 0.118$. Since
the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
scheme, consistently with what is done in NNPDF.\\
We use the following values for the mass and width of the massive particles:
% 
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}. \\
\end{equation}
We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\

>>>>

We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton 
density~\cite{Ball:2014uwa}
with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alphas\left( \MZ \right) = 0.118$. Since
the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularity are factorised with the  ${\overline{\rm MS}}$ 
scheme, consistently with what is done in NNPDF.\\
We use the following values for the mass and width of the massive particles:
% 
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is 
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}. \\
\end{equation}
We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\

The renormalisation and factorisation scales are set dynamically as
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}},
\end{equation}

### 2018-01-08 Draft/scanNLO.tex
Update scanNLO.tex
small typos fixed

\begin{figure}[hbt]
\centering
%\includegraphics[scale=0.39]{figures/scanfigures/.pdf}
FIGURE
\caption{Cross--section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics. Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
\caption{Cross--sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha_{ew}^6\alpha_s)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations. RIGHT SIDE FIG. IN PREPARATION. QUESTION: is RECOLA calc. 'exact' ?}\label{fig:ratio2d_NLO}
\end{figure}

>>>>

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}
FIGURE
\caption{Cross section (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at NLO QCD $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics. Results of \texttt{XXX} calculations.}\label{fig:mjjdyjj_2d_NLO}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}
%\includegraphics[scale=0.395]{figures/scanfigures/.pdf}
\caption{Cross sections (fb) per bin of $(M_{jj},\,\Delta y_{jj})$ at $\mathcal{O}(\alpha^6\alphas)$, without any cut on the $jj$ pair kinematics: ratio of approximated squared amplitudes over the full matrix element. The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right). Results of \texttt{VBFNLO} (approximated) and \texttt{RECOLA} (full) calculations. RIGHT SIDE FIG. IN PREPARATION. QUESTION: is RECOLA calc. 'exact' ?}\label{fig:ratio2d_NLO}
\end{figure}
